### 2021-09-05 manuscript/synthetic_data.tex
bring Val's changes in synthetic data and figures

Using the classical method (equation \ref{eq:estimated-p-parameter-space}) a predicted data
(not shown) was estimated and the data residuals are shown in Figure \ref{fig:synthetic_residuals_convergence_comparison}a, 
with mean of $0.3712$ nT and standart deviation of $0.2798$ nT.
This process took $17.10$ seconds.

@@

Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT, was $0.18$ seconds.
The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT

@@

The data residuals either using classical approach 
(Figure \ref{fig:synthetic_residuals_convergence_comparison}j) or
using our method (Figure \ref{fig:synthetic_residuals_convergence_comparison}k) reveal acceptable data fitting.
Using the classical approach, the data residuals have mean of $0.3865$ nT 
and standart deviation of $0.3216$ nT.
Using our method, the data residuals have mean of $1.6105$ nT and standart deviation of $1.6231$ nT.

@@

Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.4155$ nT and standart deviation of $0.4005$ nT. 
By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $6.622$ nT and standart deviation of $5.901$ nT.
The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison}o)
reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
the Euclidean norm of the data residuals decreases slower than previous tests

>>>>

Using the classical method (equation \ref{eq:estimated-p-parameter-space}) a predicted data
(not shown) was estimated and the data residuals are shown in Figure \ref{fig:synthetic_residuals_convergence_comparison}a, 
with mean of $0.3627$ nT and standart deviation of $0.2724$ nT.
This process took $17.10$ seconds.

@@

Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT. The processing time was $0.18$ seconds.
%The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT

@@

The data residuals either using classical approach 
(Figure \ref{fig:synthetic_residuals_convergence_comparison}j) or
using our method (Figure \ref{fig:synthetic_residuals_convergence_comparison}k) reveal acceptable data fitting.
Using the classical approach, the data residuals have mean of $0.3712$ nT 
and standart deviation of $0.2870$ nT.
Using our method, the data residuals have mean of $0.9542$ nT and standart deviation of $0.8943$ nT.

@@

Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT. 
By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison}o)
reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
the Euclidean norm of the data residuals decreases slower than previous tests
